Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
edits
abstract

%\toctitle{Lecture Notes in Computer Science}
%\tocauthor{Authors' Instructions}
\institute{}

@@

\begin{abstract}
%
We present a sound and automated approach to synthesize safe digital
feedback controllers for physical plants represented as linear, time
invariant models.  Models are described as dynamical equations with inputs,
evolving over a continuous state space and accounting for errors due to the
digitalization of signals by the controller.  The approach works in two
stages, leveraging counterexample guided inductive synthesis (CEGIS) and
reachability analysis.  CEGIS synthesizes a static feedback controller that
stabilizes the system under some restrictions given by the safety of the
reach space.  Safety is verified either via BMC or abstract acceleration; if
the verification step fails, we generate an alternative controller by
generalizing the counterexample.  We synthesize stable and safe controllers
for intricate physical plant models from the digital control literature.
%
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

@@

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix:LTIbackground}. 
All experiments were performed considering $\underline{x_{i}}=-1$ and 
$\overline{x_{i}}=1$ and the inputs $u_{k}=0, \forall k>0$.
We have conducted the experimental evaluation on a 12-core 2.40\,GHz
Intel Xeon E5-2440 with 96\,GB of RAM and Linux OS. We used the Linux \emph{times} command
to measure CPU time used for each benchmark. The experimental runtime was limited to
one hour per benchmark.
%

>>>>

%\toctitle{Lecture Notes in Computer Science}
%\tocauthor{Authors' Instructions}
\author{Anonymous}
\institute{}

@@

\begin{abstract}
%
We present a sound and automated approach to synthesize safe digital
feedback controllers for physical plants represented as linear, time
invariant models.  Models are given as dynamical equations with inputs,
evolving over a continuous state space and accounting for errors due to the
digitalization of signals by the controller.  Our approach has two stages,
leveraging counterexample guided inductive synthesis (CEGIS) and
reachability analysis.  CEGIS synthesizes a static feedback controller that
stabilizes the system under restrictions given by the safety of the reach
space.  Safety is verified either via BMC or abstract acceleration; if the
verification step fails, we refine the controller by generalizing the
counterexample.  We synthesize stable and safe controllers for intricate
physical plant models from the digital control literature.
%
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

@@

All benchmarks were discretized with different sample times using 
the approach described in Appendix~\ref{sec:appendix:LTIbackground}. 
All experiments were performed considering $\underline{x_{i}}=-1$ and 
$\overline{x_{i}}=1$ and the inputs $u_{k}=0, \forall k>0$.
We have conducted the experimental evaluation on a 12-core 2.40\,GHz
Intel Xeon E5-2440 with 96\,GB of RAM and Linux OS. We used the Linux \emph{times} command
to measure CPU time used for each benchmark. The experimental runtime was limited to
one hour per benchmark.
%
